\documentclass[10pt, letterpaper]{article}

% Packages:
\usepackage[
    ignoreheadfoot,
    top=2 cm,
    bottom=2 cm,
    left=2 cm,
    right=2 cm,
    footskip=1.0 cm,
]{geometry}
\usepackage[explicit]{titlesec}
\usepackage{tabularx}
\usepackage{array}
\usepackage[dvipsnames]{xcolor}
\definecolor{primaryColor}{RGB}{0, 79, 144}
\usepackage{enumitem}
\usepackage{fontawesome5}
\usepackage{amsmath}
\usepackage[
    pdftitle={Felippe Negr\~{a}o's Resume},
    pdfauthor={Felippe Negr\~{a}o de Oliveira},
    pdfcreator={LaTeX},
    colorlinks=true,
    urlcolor=primaryColor
]{hyperref}
\usepackage[default, type1]{sourcesanspro} 

\pagestyle{empty}
\setcounter{secnumdepth}{0}
\setlength{\parindent}{0pt}
\setlength{\columnsep}{0.15cm}

\titleformat{\section}{\Large\color{primaryColor}}{}{0pt}{\textbf{#1}\hspace{0.15cm}\titlerule[0.8pt]\hspace{-0.1cm}}

\begin{document}

\begin{center}
    {\fontsize{30 pt}{30 pt} \textbf{Felippe Negr\~{a}o de Oliveira}}
    
    \vspace{0.3 cm}
    
    {Vit\'oria, ES, Brazil \quad \faEnvelope[regular] \href{mailto:felippeno@gmail.com}{felippeno@gmail.com} \quad \faLinkedin \href{https://linkedin.com/in/felippenegrao}{felippenegrao}} 
\end{center}

\section{Summary}
Software Engineer at \textbf{Bento Ltd.} and at \textbf{INNYX Tecnologia Ltda}, working on front-end development of web projects and mobile applications with \textbf{Flutter}. Co-founder and CEO of \textbf{Mostra A\'i}, a digital showcase connecting consumers to local retailers. Experienced in software development, Mobile Architecture, and UI optimization to provide the best user experience.

\section{Professional Experience}
\textbf{Bento Ltd} \hfill \textit{September 2024 - Present}\newline
Software Engineer (Flutter), George Town, Cayman Islands - Remote
\begin{itemize}
    \item Development and optimization of cross-platform mobile applications.
    \item Designing new features and improving app interfaces.
\end{itemize}

\textbf{Mostra A\'i} \hfill \textit{March 2024 - Present}\newline
Co-Founder and CEO, Santa Teresa, ES - Remote
\begin{itemize}
    \item Development and management of the digital platform for local commerce.
    \item Growth strategies and acquisition of partner retailers.
\end{itemize}

\textbf{Minha Morada} \hfill \textit{December 2022 - October 2023}\newline
Mobile Software Architect (Flutter), Lisbon, Portugal - Remote
\begin{itemize}
    \item Led the architecture, maintenance, and implementation of new mobile app features.
    \item Collaborated with a talented team to create exceptional mobile experiences.
    \item Transformed complex challenges into practical solutions for real estate transactions.
\end{itemize}

\textbf{INNYX Tecnologia Ltda} \hfill \textit{August 2022 - Present}\newline
Mobile Software Engineer (Flutter), São Paulo, SP - Remote
\begin{itemize}
    \item Developed the Moove App Driver, enhancing UX/UI and performance.
    \item Worked as a front-end web developer on internal projects (Vue.js).
\end{itemize}

\textbf{Captis} \hfill \textit{January 2022 - May 2022}\newline
Junior Mobile Software Engineer (Flutter), Vancouver, BC, Canada - Remote
\begin{itemize}
    \item Implemented entities, gateways, repositories, and services following Domain-Driven Design.
    \item Improved the project’s UI/UX, creating widgets and intuitive features.
    \item Participated in pair programming sessions and bug fixing.
\end{itemize}

\textbf{Valença City Hall - BA} \hfill \textit{April 2018 - January 2022}\newline
Civil Engineer, Valença, BA - On-site
\begin{itemize}
    \item Developed and supervised engineering projects and municipal works.
    \item Planned, coordinated, and maintained urban infrastructure.
    \item Ensured quality control of supplies and services.
\end{itemize}

\section{Education}
\textbf{Federal University of Technology - Paraná} \hfill \textit{June 2021 - February 2025}\newline
Bachelor's in Software Engineering
\begin{itemize}
    \item GPA: 9.0/10.0
    \item \textbf{Relevant Courses:} Software Architecture, Databases, Requirements Engineering, Mobile Development.
\end{itemize}

\textbf{Estácio University} \hfill \textit{2019 - 2020}\newline
Postgraduate in Environmental Engineering and Basic Sanitation
\begin{itemize}
    \item \textbf{Relevant Courses:} Environmental Management, Water Treatment, Sustainability, and Urban Planning.
\end{itemize}

\textbf{Multivix College} \hfill \textit{2018}\newline
Specialization in Civil Construction and Structures
\begin{itemize}
    \item \textbf{Relevant Courses:} Concrete Structures, Project Analysis, Construction Project Management.
\end{itemize}

\textbf{IESLA - Latin American Higher Education Institute} \hfill \textit{January 2021 - Ongoing}\newline
Postgraduate Lato Sensu in Neuroscience and Behavior
\begin{itemize}
    \item \textbf{Relevant Courses:} Cognitive Psychology, Applied Neuroscience, Learning Processes, and Decision Making.
\end{itemize}

\textbf{Multivix College} \hfill \textit{March 2013 - December 2017}\newline
Bachelor's in Civil Engineering
\begin{itemize}
    \item GPA: 7.8/10.0
    \item \textbf{Relevant Courses:} Structural Calculation, Construction Materials, Hydraulics, Urban Planning.
\end{itemize}
    
\section{Skills and Competencies}
\textbf{Main Technologies:} Flutter, Vue.js, NestJS, AWS (S3, CodePipeline, CodeBuild, Elastic Beanstalk, EC2, Route 53, IAM), Firebase (Auth, Firestore, Crashlytics, Notifications).

\textbf{Databases:} PostgreSQL, Firestore

\textbf{Programming Languages:} Dart, C, Java, TypeScript

\textbf{Methodologies:} Kanban, DDD, CI/CD, Unit Testing

\textbf{Tools:} Git, GitFlow, Postman, Figma, ClickUp

\section{Certifications}
\begin{itemize}
    \item Flutter with Web API: Integrating Your Mobile App
    \item iOS Layout: More Features for Creating Responsive Screens
    \item Swift Part 2: UIKit, Storyboard, and the Delegate Pattern
    \item TQI Fullstack Developer
\end{itemize}

\end{document}
